preciseTAD: A machine learning framework for precise 3D domain boundary prediction at base-level resolution

### 2020-09-22 Manuscript/manuscript.Rmd
fixed grammar
moved fig2 position
added a keywords section that needs to be filled in
Changed "intro" to "background"; moved methdos section to last; added Declaration section filled in some subsections, others still need filled in

# Introduction

@@

@@

**Additional File 1**. An example script for applying Arrowhead to in situ Hi-C data (HIC001-HIC018) to obtain chromosome-specific TAD boundaries on the GM12878 cell line at 5kb, 10kb, 25kb, 50kb, 100kb resolutions. An example of deepTools commands to generate plotProfiels and plotHeatmaps is also provided.

@@

@@

# Acknowledgements

_Conflict of Interest._ None.

<!-- # Funding -->

>>>>

# Keywords

# Background

@@

# Conclusion

@@

@@

# Additional File Legends

**Additional File 1**. An example script for applying Arrowhead to in situ Hi-C data (HIC001-HIC018) to obtain chromosome-specific TAD boundaries on the GM12878 cell line at 5kb, 10kb, 25kb, 50kb, 100kb resolutions. An example of deepTools commands to generate plotProfiles and plotHeatmaps is also provided.

@@

# Declarations

## Ethics approval and consent to participate

Not applicable

## Consent for publication

Not applicable

## Availability of data and materials

All data generated or analysed during this study are included in this published article [and its supplementary information files].

## Competing interests

Not applicable

## Funding

## Authors' contributions

## Acknowledgements

## Authors' information (optional)
